%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.85]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{4cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Matthew} % Your first name
\familyname{Coolbeth} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Software Engineer and  Computer Scientist}
\address{2746 Hebron Ave}{Glastonbury, CT 06033}

\phone{(860) 420 2024}
\email{coolbeth@gmail.com}

% The first argument is the url for the clickable link, the second argument is the 
% url displayed in the template - this allows special characters to be displayed such
% as the tilde in this example
%\homepageone{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} 
%\homepagetwo{https://www.linkedin.com/in/mac01021}
%			{https://www.linkedin.com/in/mac01021} 
\homepageone{https://github.com/mac01021}
			{https://github.com/mac01021}
%\homepagethree{https://play.google.com/store/apps/developer?id=mac01021}	 
%			  {https://play.google.com/store/apps/developer?id=mac01021} 


%\homepagefour{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} 

%\extrainfo{More stuff}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}





%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage
%
%%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\recipient{~}{~}
%\date{\today} % Letter date
%\opening{To whom this may concern,} % Opening greeting
%\closing{Sincerely,} % Closing phrase
%\enclosure[Attached]{r\'{e}sum\'{e}{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%\lipsum[1-3] % Dummy text
%
%
%\makeletterclosing % Print letter signature
%
%
%\newpage
%----------------------------------------------------------------------------------------
%	CV
%--------------------------------------------------------------------------------------
\makecvtitle % Print the CV title


\vspace{-1.5cm}
\section{Professional Experience}

\cventry{Feb 2017 - Present}{Data Engineer}{\textsc{HYP3R}}{}{}{
    \begin{itemize}
        \item Designed, built, and maintained mission critical "Ingestion Engine"
            providing the company's core product with realtime social media content
            from millions of feeds.
        \item Prototyped and shipped machine learning system to determine what social
            media posts originate from a venue of interest.
        \item Codesigned storage tier and REST API backing the company's new flagship
            application, serving queries over a dataset of billions of posts.
        \item Used AWS, Docker, Kinesis, Avro, Java, Scala, Akka, PostgreSQL, Cassandra, Spark, Elasticsearch, DynamoDB,
            Golang, Clojure
    \end{itemize}
}

\cventry{Feb 2015 - Feb 2017}{Software Engineer}{\textsc{ESPN}}{}{}{
    \begin{itemize}
        \item Architected and implemented core components of infrastructure to ingest
            realtime updates from sporting events, delivering the latest game information to the TV
            studio as well as to the espn.com website.
        \item Built, maintained, and troubleshot pipelines of microservices communicating via messages
            over Apache Kafka.
        \item Implemented functionality equivalent to Kafka's consumer groups using Apache Zookeeper.
        \item Used Zookeeper, Kafka, Avro, AWS, Java, Maven, Golang, Clojure
    \end{itemize}
}

\cventry{Aug 2010 -- Feb 2015}{Applications Developer}{\textsc{University of Connecticut}}{}{}{
    \begin{itemize}
        \item Built enterprise web applications using Python MVC frameworks
        \item Extensive automated testing - code coverage around 98\%
        \item Used Python, MS SQL Server, SQLAlchemy, Pylons, Pyramid
    \end{itemize}
}


\cventry{Jan 2010 -- Aug 2010}{Software Developer}{\textsc{QueBIT Consulting, LLC}}{}{}{
	\begin{itemize}
		\item Prototyped a web application for double-entry book keeping based on the
			IBM COGNOS TM1 database system.
		\item Built Excel plugin to populate a journal template in an excel spreadsheet from TM1.
		\item These products later evolved into QueBIT's "ControlWORQ" product.
		\item Used C\#, ASP.NET, SOAP, MySQL, TM1, VBA, .NET APIs for MS Excel.
	\end{itemize}
}

\cventry{Sep 2009 -- Dec 2009}{Software Developer (Contractor) }{\textsc{Pfizer, Inc}}{}{}{
	Developed a Java EE web application to process sets of nucleotide sequences for research biologists.
	\begin{itemize}
		\item Collaborated with genomics researchers to develop and refine application requirements.
		\item The application accepts zip files produced by DNA sequencers, converts each nucleotide
			sequence to an amino acid sequence, executes an external process to generate a
			multi-sequence alignment, and then generates a report depicting each alignment.
		\item Used Java 6 EE, Tomcat, JSP, BioJava, HMMER, JQuery.
	\end{itemize}
}

\cventry{Jan 2008 -- Aug 2009}{Research Specialist}{\textsc{University of Connecticut}}{}{}{
	Worked in an interdepartmental research group to build two energy-demand-forecasting
			systems for ISO New England.
	\begin{itemize}
		\item Prototyped forecasting methods incorporating signal processing and
			machine learning techniques (wavelet decomposition \& neural networks).
		\item Primary Java developer for two forecasting engines: one short-term (days) and one
			very short term (hourse).  The later system was later open-sourced.
		\item Used Java 6, Swing, C++, Oracle, Perst (embedded database), Git, CVS.
	\end{itemize}
}

\cventry{Aug 2007 -- Dec 2007}{Teaching Assistant}{\textsc{University of Connecticut}}{}{}{
	\begin{itemize}
		\item Instructed weekly lab activity for a freshman-level computer programming course.
		\item Tutored undergraduate students in areas related to computer science and mathematics.
	\end{itemize}
}



\section{Education}

\cventry{2009}{MS - Computer Science \& Engineering}{University of Connecticut}{}{}{}  % Arguments not required can be left empty
\cventry{2007}{BS - Computer Science}{University of Connecticut}{}{}{}



%%\newpage
%%\section{Programming Tools \& Practices}
%%
%%\cvitem{Version Control:} {\textsc{Git, Subversion, CVS, Mercurial}}
%%\cvitem{Programming Languages:}{\textsc{C/C++, C\#, Go, Java, Javascript, MATLAB, Python, Scala, SQL,} et cetera}
%%\cvitem{Database Systems:} {\textsc{MS SQL Server, MySQL, Oracle, SQLite}}
%%\cvitem{MVC Frameworks:}{\textsc{Spring, Play!, Pylons, Pyramid}}
%%\cvitem{ORMs:}{\textsc{SQLAlchemy, Hibernate}}
%%\cvitem{Build Tools:}{\textsc{Gradle, Ant, Make}}
%%\cvitem{Web Technologies:}{\textsc{REST, AJAX, Websockets}}
%%\cvitem{Javascript Frameworks:}{\textsc{JQuery, Backbone, AngularJS}}
%%\cvitem{GUI Frameworks:}{\textsc{Android, Swing, GTK}}
%%\cvitem{Engineering Practices:}{\textsc{Agile, SCRUM, Continuous Integration, Test-Driven Development}}
%%
%%{\em I am probably omitting something of interest.  Ask me about your favorite tool or practice.}

\begin{thebibliography}{1}

	\bibitem{stlf} {\em Short-term Load Forecasting: Similar Day-Based Wavelet Neural Networks}
		(Y. Chen, P. B. Luh, Y. Zhao, L. D. Michel, M. A. Coolbeth, P. B. Friedland, \& S. J. Rourke)
		{\em In IEEE Transactions on Power Systems, volume 25, 2010}.

	\bibitem{vstlf} {\em Very Short-term Load Forecasting: Multilevel Wavelet Neural Networks with Data
		Pre-filtering}
		(C. Guan, P. B. Luh, L. D. Michel, M. A. Coolbeth, Y. Zhao, Y. Chen, C. J. Manville, P. B. Friedland,
		\& S. J. Rourke)
		{\em In Proceedings of the 2009 PESGM, 2009}.

	\bibitem{data-collection} {\em Data Collection with Multiple Sinks in Wireless Sensor Networks} 
		(S. Chen, M. Coolbeth, H. Dinh, Y. A. Kim, \& B. Wang)
		{\em In Proceedings of the 2009 conference on Wireless Algorithms, Systems, and Applications, 2009}.

\end{thebibliography}


\end{document}
